DeepSphere: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2019-03-19 scnn.tex
cite paper which could not use Cohen's spherical CNN for CMB analysis

Ideally, we would compare DeepSphere to alternative spherical CNNs like \citep{cohen2018sphericalcnn} and \citep{esteves2017sphericalcnn}.
There are however two issues with that comparison.
First, these CNNs were developed for the equirectangular sampling.
An option is to modify the available implementations to use HEALPix, which is a major undertaking due to their complexity.
Another option is to transform the cosmological maps to the equirectangular sampling, which is of disputable usefulness as the field is unlikely to use that sampling.
% nefieldfully to not introduce artifacts
Second, those methods, based on SHTs, only work on the full sphere (at least in their current state).
As shown in \figref{filtering_speed}, using the full sphere at a resolution of $N_{side} = 1024$ would result in a slow-down of multiple orders of magnitude compared to using a partial graph.\footnote{Note that the authors report results for maps of at most $(2 \times 128)^2 = 65,536$ pixels \citep{cohen2018sphericalcnn, esteves2017sphericalcnn}.
That is the size of our smallest partial map, while the largest is of approximately one million pixels.}
For those reasons and because we think that a proper comparison is better carried out on diverse datasets and tasks, we leave it as future work.

>>>>

Ideally, we would compare DeepSphere to alternative spherical CNNs like \citep{cohen2018sphericalcnn} and \citep{esteves2017sphericalcnn}.
There are however two issues with that comparison.
First, these CNNs were developed for the equirectangular sampling.
An option is to modify the available implementations to use HEALPix, which is a major undertaking due to their complexity.
Another option is to transform the cosmological maps to the equirectangular sampling, which is of disputable usefulness as the field is unlikely to use that sampling.
% transformation must be carefully handled to not introduce artifacts
Second, those methods, based on SHTs, only work on the full sphere (at least in their current state).
As shown in \figref{filtering_speed}, using the full sphere at a resolution of $N_{side} = 1024$ would result in a slow-down of multiple orders of magnitude compared to using a partial graph.
The authors of \citep{he2018cmbdl} could not use \citep{cohen2018sphericalcnn} for CMB analysis because of that.\footnote{Note that reported results in \citep{cohen2018sphericalcnn} and \citep{esteves2017sphericalcnn} are for maps of at most $(2 \times 128)^2 = 65,536$ pixels.
That is the size of our smallest partial map, while the largest is of approximately one million pixels.}
For those reasons and because we think that a proper comparison is better carried out on diverse datasets and tasks, we leave it as future work.
